\clearpage
\sffamily
{\bfseries\color[rgb]{0.4,0.4,0.4}{Law 13 -- Free Kicks} }
\phantomsection
\addcontentsline{toc}{section}{Law 13 -- Free Kicks}

\bigskip

{\bfseries Types of free kick}

\headlinebox

Free kicks are either direct or indirect.

\bigskip

{\bfseries The direct free kick }

\headlinebox

Ball enters the goal:

\begin{itemize}
\item if a direct free kick is kicked directly into the
opponents{\textquoteright} goal, a goal is awarded
\item if a direct free kick is kicked directly into the team's own goal, a corner kick is awarded to the opposing team
\end{itemize}

\bigskip

{\bfseries The indirect free kick}

\headlinebox

\greyed{(suspended:
Signal

The referee indicates an indirect free kick by raising his arm above his head. He maintains his arm in that position until the kick has been taken and the ball has touched another player or goes out of play.)}


\bigskip

Ball enters the goal

A goal can be scored only if the ball either moves 20 cm from the free-kick point or has been touched by another player before being kicked into the goal \greyed{(replaces: subsequently touches another player before it enters the goal)}:

\begin{itemize}
\item if an indirect free kick is kicked directly into the
opponents' goal, a goal kick is awarded
\item if an indirect free kick is kicked directly into the
team's own goal, a corner kick is awarded to the
opposing team
\end{itemize}

\bigskip

{\bfseries Procedure}

\headlinebox

(new) Signal

The referee blows the whistle, announces 'Free-Kick' cyan or Magenta (Blue or Red) and then  places the ball depending on the call. The assistant referee who operates the game controller clicks on Free Kick Cyan/Magenta Ready. 

For both direct and indirect free kicks, the ball must be stationary when the kick is taken 
\greyed{(suspended: and the
kicker must not touch the ball again until it has touched another player)}.

\bigskip

{\bfseries Position of free kick }

\headlinebox

Free kick inside the penalty area

Direct or indirect free kick to the defending team:

\begin{itemize}
\item all opponents must be at least 0.5 m from the ball. (new:) Players have a maximum of 15 seconds to move away from the ball. Any opponent robot still closer than 50cm is considered as an incapable player and must be removed from the field for 30 seconds removal penalty.
\greyed{(replaces: all opponents must be at least 9.15 m (10 yds) from the ball )}
\item all opponents must remain outside the penalty area until the ball is in play
\item the ball is in play when it is kicked directly out of the penalty area (new): or 10 seconds after the referee gave the signal
\item a free kick awarded in the goal area may be taken from any point inside that area
\end{itemize}

\bigskip

Indirect free kick to the attacking team:

\begin{itemize}
\item all opponents must be at least 0.5 m from the ball until it is in play, unless they are on their own goal line between the goalposts. (new:) Players have a maximum of 15 seconds to move away from the ball. Any opponent robot still closer than 50cm and not at the goal line is considered as an incapable player and must be removed from the field for 30 seconds removal penalty.
\greyed{(replaces: all opponents must be at least 9.15 m (10 yds) from the ball until it is in play, unless they are on their own goal line between the goalposts)}
\item the ball is in play when it is kicked and moves (new): or 10 seconds after the referee gave the signal
\item an indirect free kick awarded inside the goal area must be taken on the goal area line parallel to the goal line at the point nearest to where the infringement occurred
\end{itemize}

\bigskip

Free kick outside the penalty area:

\begin{itemize}
\item all opponents must be at least 0.5 m from the ball until it is in play. (new:) Players have a maximum of 15 seconds to move away from the ball. Any opponent robot still closer than 50cm is considered as an incapable player and must be removed from the field for 30 seconds removal penalty.
\greyed{(replaces: all opponents must be at least 9.15 m (10 yds) from the ball until it is in play )}
\item the ball is in play when it is kicked and moves (new): or 10 seconds after the referee gave the signal
\item the free kick is taken from the place where the infringement occurred or from the position of the ball when the infringement occurred (according to the infringement)
\end{itemize}

\bigskip

{\bfseries Infringements and sanctions}

\headlinebox

If, when a free kick is taken, an opponent is closer to the ball than the required distance:

\begin{itemize}
\item the opponent receives a 30 second removal penalty \greyed{(replaces: the kick is retaken)}
\end{itemize}

If, when a free kick is taken by the defending team from inside its own penalty area, the ball is not kicked directly out of the penalty area:


\begin{itemize}
\item the kick is retaken (new:) if the \removed{goal keeper} \added{robot performing the kick} managed to reach the ball within the time frame. Otherwise, the ball is in play again.
\end{itemize}

\bigskip

Free kick taken by a player other than the goalkeeper

If, after the ball is in play, the kicker touches the ball again \removed{(except with his hands)} before it has touched another player (new) or before it was moved for at least 20 cm:

\begin{itemize}
\item an indirect free kick is awarded to the opposing team, to be taken from the place where the infringement occurred (see Law 13 -- Position of free kick)
\end{itemize}

\bigskip

If, after the ball is in play, the kicker deliberately handles the ball before it has touched another player (new) or before it was moved for at least 20 cm:

\begin{itemize}
\item a direct free kick is awarded to the opposing team, to be taken from the place where the infringement occurred (see Law 13 -- Position of free kick)
\item a penalty kick is awarded if the infringement occurred inside the kicker's penalty area
\end{itemize}

\bigskip

Free kick taken by the goalkeeper

If, after the ball is in play, the goalkeeper touches the ball again (except with his hands), before it has touched another player (new) or before it was moved for at least 20 cm:

\begin{itemize}
\item an indirect free kick is awarded to the opposing team, to be taken from the place where the infringement occurred (see Law 13 -- Position of free kick)
\end{itemize}

\bigskip

If, after the ball is in play, the goalkeeper deliberately handles the ball before it has touched another player (new) or before it was moved for at least 20 cm:

\begin{itemize}
\item a direct free kick is awarded to the opposing team if the infringement occurred outside the goalkeeper's penalty area, to be taken from the place where the infringement occurred (see Law 13 -- Position of free kick)
\item an indirect free kick is awarded to the opposing team if the infringement occurred inside the goalkeeper's penalty area, to be taken from the place where the infringement occurred (see Law 13 -- Position of free kick)
\end{itemize}

\bigskip

(new) If a free kick was awarded to team A and any player of team A touches the ball before the referee announced the execution of the free kick:

\begin{itemize}
\item The ball is in play.
\item The player touching the ball received a warning. For the second warning, the player received a yellow card. For the fourth warning, the player receives a second yellow card.
\end{itemize}

\bigskip

(new) If a free kick was awarded to team A and any player of team B touches the ball before the referee announced the execution of the free kick:

\begin{itemize}
\item The free kick is retaken.
\item The player touching the ball received a warning. For the second warning, the player received a yellow card. For the fourth warning, the player receives a second yellow card.
\end{itemize}
