\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{pgfornament}

\title{Rule Changes Intended for 2021}
\date{\vspace{-12ex}}

\begin{document}

\maketitle

\begin{center}
    \pgfornament[scale=0.4]{88}

\end{center}

\section{Changes Accepted via Previous Vote or RoadMap }
Changes in this section have either been accepted via a vote in the previous year or they are given by the RoadMap.

\begin{enumerate}
    \item A \textbf{minimum WiFi quality} will be added to the rule book (specifications will be discussed)
    \item Robots out of play will not be allowed to communicate with robots in play. In order to enforce this rule, \textbf{messages send by robots being currently out of play will be automatically filtered} from being broadcasted. This will require to make certain fields in the message protocols mandatory. Details will be further discussed for 2021.
\end{enumerate}

\section{Changes Requiring Further Discussions}
Changes in this section will be brought up for discussion and voting in the next year again.

\begin{enumerate}
    \item The \textbf{minimum height of AdultSize robots} may be increased again.
    \item A \textbf{fair play rule} similar to other leagues may be introduced. This rule shall ensure that games should be played according to a fair and common-sense understanding of soccer.
    \item The \textbf{Push-Recovery challenge in AdultSize} may be replaced by the collaborative localization challenge.
    \item For the \textbf{Kick from Moving Ball Challenge}, the pass may only be allowed to be performed by another robot.
\end{enumerate}{}

\end{document}