\clearpage
\sffamily
{\bfseries\color[rgb]{0.4,0.4,0.4} Part G: Long Stride Challenge}
\phantomsection
\addcontentsline{toc}{subsection}{Part G: Long Stride Challenge}
\added{

\bigskip

In this challenge the robot must "step over" a measured distance on the ground.

\vspace{2em}
{\bfseries Setup}

A length of string is placed on the ground at a known distance from the center line of the field.

\vspace{2em}
{\bfseries Execution}
\begin{enumerate}
\item The robot is placed on the other side of the ceneter line, facing the string.
\item The robot steps over the region from the center line to the far side of the string.

\end{enumerate}
\vspace{2em}
{\bfseries Evaluation}
\begin{itemize}
\item Failure
\begin{itemize}
\item The robot steps within the area between the string and the center line.
\end{itemize}
\item Partial success
\begin{itemize}
\item The robot steps over the distance but touches the string or the center line.
\end{itemize}
\item Success
\begin{itemize}
\item The robot steps with both feet over the string without touching either the string or the center line.
\end{itemize}
\end{itemize}



\vspace{2em}
{\bfseries Ranking}\\
The distance between the string and the center line is measured and divided by the length of the robot's leg to give a normalized score.
Teams are ranked on their best run according to the following criteria:
\begin{enumerate}
\item The distance of a \textit{Successful} run
\item The distance of a \textit{Partially Successful} run
\end{enumerate}}