\clearpage
\sffamily
{\bfseries\color[rgb]{0.4,0.4,0.4}
The Trend in Rule Evolution for the Next Years }

\bigskip

In this section the Technical Committee (TC) wants to make explicit the trends to be followed in the rules in the next years in order to improve the scientific level of the robots developed by the RoboCup teams. The evolution of rules in the humanoid league has been following
a biennial schedule where major changes (like the number of players per team) have been introduced every two years and only incremental changes every other year.

\bigskip

{\bfseries The Layout of the Field}

\headlinebox

Size of the playing field is intended to increase to 20 meters * 12 meters in the year 2020.

\bigskip

{\bfseries The Design of the Robots}

\headlinebox

The height of the robots, the minimum size of KidSize robots and the overlap between size classes may be increased in the future.
\bigskip

\added{Similar to the basic equipment of human soccer players, robot's will be required to wear a jersey or shirt (or vest as a preliminary solution envisioned for 2019) which identifies the player with a team color and individual number. }

\bigskip

{\bfseries Handling of the robots.}

\headlinebox

In the future (envisioned for the year \removed{2018}\added{2019}), robot players will be untangled and removed from the field in the respective cases by assistant referees in order to limit the number of humans on the field. In order to facilitate this, the robots must feature a handle in the neck area and must be designed in a way that they tolerate to be lifted vertically by this handle without taking harm or causing harm to the handler.

\bigskip

In the future the involvement of robot handlers for the AdultSize sub-league will be reduced. AdultSize robots should become more and more robust and autonomous over the coming years.

\bigskip

{\bfseries Laws of the Game}

\headlinebox

The number of players in soccer games will be increased. This is to encourage team play and cooperation among humanoid robots.

\bigskip

\added{Envisioned for 2019, the simplified penalty kick procedure of Law 14 will be suspended and replaced by the regular penalty kick as defined in the FIFA rule book.}

\bigskip

{\bfseries Acknowledgements}

\headlinebox

These rules evolved from previous versions of the RoboCup Humanoid League rules. We would like to thank Henry Yen for the conversion of the rules into a basic LaTeX version in 2010. The 2008 version of the rules was compiled by Pasan Kulvanit and Oskar von Stryk, the 2007 version of the rules by Emanuele Menegatti and the 2006 version by Sven Behnke, who did a remarkable job improving the rule document and gearing it towards the FIFA Laws of the Game. The improvements of the 2005 version were compiled by Norbert Michael Mayer. Other input came earlier from the rules of the RoboCup MiddleSize and Four-Legged Leagues.

The rules were continuously discussed within the technical committee of the humanoid league and also on the humanoid league mailing list. The following members of the technical committee for 2018 were responsible for the rule evolution: Jacky Baltes, Reinaldo Bianchi, Sander van Dijk, Hafez Farazi, Reinhard Gerndt, Lodvic Hofer, Maike Paetzel and Soroush Sadeghnejad. Special thanks go to Martin Friedmann and Sebastian Mielke for the contribution of several figures and to Philipp Allgeuer for helping with the conversion of the 2017 rule book to LaTeX and his contributions to the 2018 version of the rules.
